<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>
---
title: "janitor package clean names example"
author: "Matt Pettis (matthew.pettis@gmail.com)"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: no
---

```{r setup, include=FALSE}
# Style chunk above from: https://stackoverflow.com/questions/34906002/increase-width-of-entire-html-rmarkdown-output?rq=1
knitr::opts_chunk$set(echo = TRUE)
```


# Setup

Load the data and merge as needed.

```{r echo=FALSE}
# options(width = 120)
options(width = 144)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(purrrlyr))
suppressPackageStartupMessages(library(purrr))
suppressPackageStartupMessages(library(rprojroot))
suppressPackageStartupMessages(library(janitor))

# Setup ------------------------------------------------------------------------
# Get the project root directory
dir_proj <- find_root(has_file("PROJECT_ROOT"))
```


# Summary

Just a quick run-through of the `janitor` package.  Found here: https://github.com/sfirke/janitor





# Bulk name changes, first example



## Data load
```{r}
df_main <- read_csv(file.path(dir_proj, "dat", "ex_10.csv"), col_types = cols())
```



## Look at the data and names
```{r}
df_main
```



## Clean the names, save original names

Save off the original names
```{r}
v_main_colnames_orig <- names(df_main)
```



Change the names to clean names
```{r}
df_main <- df_main %>%
  clean_names()
```


Make a mapping from new names back to their original names
name -> value :: new-name -> original name
```{r}
kv_original_names <- set_names(v_main_colnames_orig
                               , names(df_main))
  
```

Look at name mapping
```{r}
kv_original_names %>%
  enframe()
```


Now we can use column names as identifiers in our language easily
```{r}
df_main %>%
  select(el_sylla_qaaid)
```







# Bulk name changes, second example

Here are some funky columnnames to use
```{r}
v_grungy_colnames <- c(
  "with a division / sign and spaces"
  , "% sign in there"
  , "this (has) parethesis"
  , "a newline\nembedded in it"
  , "duplicated colname"
  , "duplicated colname"
)
v_grungy_colnames %>% walk(~ cat(.x, "\n\n"))
```



Make a dataframe with the names.
```{r}
df_ex_2 <- map(seq_along(v_grungy_colnames), ~ rnorm(5)) %>%
  as.data.frame() %>%
  setNames(v_grungy_colnames)
df_ex_2
```


Clean up the colnames
```{r}
df_ex_2 <- df_ex_2 %>%
  clean_names()
df_ex_2
```

Don't forget to make a mapping of the names
```{r}
kv_original_names_ex_2 <-
  set_names(v_grungy_colnames, names(df_ex_2))
enframe(kv_original_names_ex_2)
```





# Using lib of load functions

If I use the convention that library files of functions start with `lib-` in the `src` directory, then I can bulk-source their contents with the following:
```{r}
# Source library functions
list.files(file.path(dir_proj, "src"), pattern = "lib-.*\\.R$", full.names = TRUE) %>%
  walk( ~ source(.x))
```



Then I can load files as I want them, and have figured out the coltypes:
```{r}
load_ex_50_csv()
```


If I want the name mapping returned when I load it, I pass the flag:
```{r}
lst_temp <- load_ex_50_csv(.full_info = TRUE)

lst_temp %>% names()

lst_temp$name_map
lst_temp$data
```

